Spectral Lags in Very High Energy Emission of Gamma Ray Bursts

### 2013-11-25 gammaRays.tex
computed observations in the fraction test

Our set of parameters led to a sample you can see on the figure \ref{fig:kappaDistribution}. However, the error margins of the observed stretching factors are too large to use the KS-test on them. Nevertheless, It appears that our model doesn't contradict existing observations.

@@

Our final test is to calculate the fraction of the observable bursts which can be observed at the energies of GeV and above.

To do so, we need to compute the number of bursts visible in a given energy range, which is the integral over space and jet directions:
\begin{align}
b\left(\omega_1,\omega_2\right) &= \int_0^{z_\text{max}\left(\omega_1,\omega_2\right)} \dif V\left(z\right) \rho\left(z\right) \int_0^{\chi_\text{max}\left(z,\omega_1,\omega_2\right)} 2\pi \sin\chi \dif\chi \nonumber\\
&\approx 2\pi \int_0^{z_\text{max}\left(\omega_1,\omega_2\right)} \dif V\left(z\right) \rho\left(z\right) \int_0^{\chi_\text{max}\left(z,\omega_1,\omega_2\right)} \chi \dif\chi = \pi \int_0^{z_\text{max}\left(\omega_1,\omega_2\right)} \dif V\left(z\right) \rho\left(z\right) \chi^2_\text{max}\left(z,\omega_1,\omega_2\right)
\end{align}
Here $z_\text{max}\left(\omega_1,\omega_2\right)$ and $\chi_\text{max}\left(z,\omega_1,\omega_2\right)$ are the same values we used in the previous section: the maximum redshift from which a burst can be observed, and the maximum off-axis angle with which the burst at redshift $z$ can be observed.

The fraction in question is simply the ratio of these:
\begin{equation}
f\left(\omega_1,\omega_2,\omega_3\right) = \frac{b\left(\omega_2,\omega_3\right)}{b\left(\omega_1,\omega_3\right)} = \frac{\int_0^{z_\text{max}\left(\omega_2,\omega_3\right)} \dif V\left(z\right) \rho\left(z\right) \chi^2_\text{max}\left(z,\omega_2,\omega_3\right)}{\int_0^{z_\text{max}\left(\omega_1,\omega_3\right)} \dif V\left(z\right) \rho\left(z\right) \chi^2_\text{max}\left(z,\omega_1,\omega_3\right)}
\end{equation}

The ratio for our set of parameters is $f_m \approx 0.072$. The ratio computed from observations is $f_o = ...$. The binary distribution gives us the probability for it to happen:
\begin{equation}
...
\end{equation}
which means that the model fits observations in this test.

>>>>

Our set of parameters led to a sample you can see on the figure \ref{fig:kappaDistribution}. However, the error margins of the observed stretching factors are too large to use the KS-test on them. Nevertheless, it appears that our model doesn't contradict existing observations.

@@

Out final test is the comparison of answers to this question: given the bursts which were observed in a high energy range $\left(\omega_1,\omega_3\right)$, which fraction of them can also be observed in a very high energy range $\left(\omega_2,\omega_3\right)$?

To calculate this value, we need to compute the number of bursts visible in a given energy range, which is the integral over space and jet directions:
\begin{align}
b\left(\omega_1,\omega_2\right) &= \int_0^{z_\text{max}\left(\omega_1,\omega_2\right)} \dif V\left(z\right) \rho\left(z\right) \int_0^{\chi_\text{max}\left(z,\omega_1,\omega_2\right)} 2\pi \sin\chi \dif\chi \nonumber\\
&\approx 2\pi \int_0^{z_\text{max}\left(\omega_1,\omega_2\right)} \dif V\left(z\right) \rho\left(z\right) \int_0^{\chi_\text{max}\left(z,\omega_1,\omega_2\right)} \chi \dif\chi = \pi \int_0^{z_\text{max}\left(\omega_1,\omega_2\right)} \dif V\left(z\right) \rho\left(z\right) \chi^2_\text{max}\left(z,\omega_1,\omega_2\right)
\end{align}
Here $z_\text{max}\left(\omega_1,\omega_2\right)$ and $\chi_\text{max}\left(z,\omega_1,\omega_2\right)$ are the same values we used in the previous section: the maximum redshift from which a burst can be observed in a given energy range, and the maximum off-axis angle with which the burst at redshift $z$ can be observed.

The fraction we want to compute is the ratio of these integrals:
\begin{equation}
f\left(\omega_1,\omega_2,\omega_3\right) = \frac{b\left(\omega_2,\omega_3\right)}{b\left(\omega_1,\omega_3\right)} = \frac{\int_0^{z_\text{max}\left(\omega_2,\omega_3\right)} \dif V\left(z\right) \rho\left(z\right) \chi^2_\text{max}\left(z,\omega_2,\omega_3\right)}{\int_0^{z_\text{max}\left(\omega_1,\omega_3\right)} \dif V\left(z\right) \rho\left(z\right) \chi^2_\text{max}\left(z,\omega_1,\omega_3\right)}
\end{equation}

The ratio for our set of parameters is $f_m = 0.072$. The LAT burst catalog \ref{LATbc} contains $n = 35$ bursts, $3$ of which were observed in the energy range ${1\text{GeV}, \infty}$. So the ratio is $f_o = \frac{3}{35} \approx 0.086$. The binary distribution gives us the probability for it to happen:
\begin{equation}
\text{Pr}\left(k_o = k\right) = \frac{n}{k} f^k \left(1-f\right)^{n-k} \approx 0.223585
\end{equation}
which means that the model doesn't contradict observations in this test.
